### 2015-06-27 2015-compmorphon-morphver/poster.tex
switch logo placement?
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@61096 72bbbca6-d526-0410-a7d9-f06f51895060

	\begin{poster}{
		grid=false,
		%eyecatcher=false,
		borderColor=bordercol,
		headerColorOne=headercolone,
		headerColorTwo=headercoltwo,
		%headerColorOne=blue,
		%headerFontColor=white,
		% Only simple background color used, no shading, so boxColorTwo isn't necessary
		boxColorOne=boxcolor,
		headershape=roundedright,
		headerborder=open,
		headerheight=0.1\textheight,
		%headershape=roundedright,
		%headershade=plain,
		%headerfont=\Large\textsf, %Sans Serif
		%headerfont=\Large\sf\bf,
		textborder=rectangle,
		%background=plain,
		%background=user,
		background=none,
		headerborder=open,
		boxshade=plain,
		textborder=roundedleft,
		columns=4,
	}{ %Eye Catcher, empty if option eyecatcher=false - unused
		\includegraphics[height=6.5em]{uitlogo}
		\hspace{2cm}\begin{minipage}[t]{9em}
			\vspace{-2cm}
			\noindent\includegraphics[height=4.2em]{DCU_logo_2col}\\
			\vspace{-0.5ex}\hspace{0.105cm}\includegraphics[height=2.15em]{DCU_2010_Name_Mark_289}
			\end{minipage}
			\hspace{2cm}\includegraphics[height=6.5em]{iu_tab}
	}{ %Title (centered top)
		{\vspace{0pt}\hspace{1cm}
			{\titlefont \textsc{Finite-state morphologies and text corpora\\as resources for improving morphological descriptions}}}
	}{ %Authors (centered top, below title)
		\vspace{-0.5em}
		\begin{center}
			\begin{minipage}[t]{9em}
				\begin{spacing}{0.4}
				{Francis M.\ Tyers}\\
				{\footnotesize UiT Norgga Árktalaš Universitehta \\\texttt{francis.tyers@uit.no}}
				\end{spacing}
			\end{minipage}
			\begin{minipage}[t]{9.5em}
				\begin{spacing}{0.4}
					{Tommi Pirinen\vphantom{y}}\\
					{\footnotesize Ollscoil Chathair Bhaile Átha Cliath\\\texttt{FIXME Flammie}}
				\end{spacing}
			\end{minipage}
			\begin{minipage}[t]{12em}
				\begin{spacing}{0.4}
					{Jonathan North Washington}\\
					{\footnotesize Indiana University\\\texttt{jonwashi@indiana.edu}}
				\end{spacing}
			\end{minipage}
		\end{center}
	}{ %More eye catchers, on the right side
		\includegraphics[angle=90,height=6.5em]{apertium5b}%\hspace{-2em}
	}

>>>>

	\begin{poster}{
		grid=false,
		%eyecatcher=false,
		borderColor=bordercol,
		headerColorOne=headercolone,
		headerColorTwo=headercoltwo,
		%headerColorOne=blue,
		%headerFontColor=white,
		% Only simple background color used, no shading, so boxColorTwo isn't necessary
		boxColorOne=boxcolor,
		headershape=roundedright,
		headerborder=open,
		headerheight=0.1\textheight,
		%headershape=roundedright,
		%headershade=plain,
		%headerfont=\Large\textsf, %Sans Serif
		%headerfont=\Large\sf\bf,
		textborder=rectangle,
		%background=plain,
		%background=user,
		background=none,
		headerborder=open,
		boxshade=plain,
		textborder=roundedleft,
		columns=4,
	}{ %Eye Catcher, empty if option eyecatcher=false - unused
		\includegraphics[angle=90,height=6.5em]{apertium5b}%\hspace{-2em}
	}{ %Title (centered top)
		{\vspace{0pt}\hspace{1cm}
			{\titlefont \textsc{Finite-state morphologies and text corpora\\as resources for improving morphological descriptions}}}
	}{ %Authors (centered top, below title)
		\vspace{-0.5em}
		\begin{center}
			\begin{minipage}[t]{9em}
				\begin{spacing}{0.4}
				{Francis M.\ Tyers}\\
				{\footnotesize UiT Norgga Árktalaš Universitehta \\\texttt{francis.tyers@uit.no}}
				\end{spacing}
			\end{minipage}
			\begin{minipage}[t]{9.5em}
				\begin{spacing}{0.4}
					{Tommi Pirinen\vphantom{y}}\\
					{\footnotesize Ollscoil Chathair Bhaile Átha Cliath\\\texttt{FIXME Flammie}}
				\end{spacing}
			\end{minipage}
			\begin{minipage}[t]{12em}
				\begin{spacing}{0.4}
					{Jonathan North Washington}\\
					{\footnotesize Indiana University\\\texttt{jonwashi@indiana.edu}}
				\end{spacing}
			\end{minipage}
		\end{center}
	}{ %More eye catchers, on the right side
		\includegraphics[height=6.5em]{uitlogo}
		\hspace{2cm}\begin{minipage}[t]{9em}
			\vspace{-2cm}
			\noindent\includegraphics[height=4.2em]{DCU_logo_2col}\\
			\vspace{-0.5ex}\hspace{0.105cm}\includegraphics[height=2.15em]{DCU_2010_Name_Mark_289}
			\end{minipage}
			\hspace{2cm}\includegraphics[height=6.5em]{iu_tab}
	}
